\bf Teaching analysis reproducibility with accessibility: Enriching secondary documentation to support skill level diversity of users.

### 2022-02-10 jsdse/Manuscript.tex
reorganizing figure

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig-tree.png}
\end{center}
\caption{A phylogenetic tree from our tutorial website, extracted using OpenTree of Life tools and the rotl R package. \label{fig:second}}
\end{figure}

@@

A practice that has become more and more widespread in programming-language pedagogical practices
is the use of typos and mistakes to normalize them for learners, and show them how
to solve them when they are outside the classroom \citep{shannon2015live}.
Yet, this is rarely done on written pedagogical materials.
Primary documentation focuses on demonstrating usage function with examples that
work seamlessly, without errors. We argue that the opposite is needed to support
adoption of reproducible workflows and support long term independence in learners
\citep{gaspar2007restoring}.
We demonstrate examples that do not work
as expected and exemplify ways to address them (Figure \ref{fig:first}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig1.png}
\end{center}
\caption{Snapshot of a section of the tutorial website, where we demonstrate a common error. \label{fig:first}}
\end{figure}

@@

Besides avoiding formal language, and incorporating elements of pop culture, such as picture
character icons known as ``emojis``, to make the language more familiar to a
broader target audience (see Figure \ref{fig:first}), we made an effort to specifically
complement the primary documentation by identifying
computational concepts that were assumed or were not explained in depth.
We vetted the tutorials through feedback from workshop participants as well as individual users.
We choose examples that are charismatic for the audience.
For example, when we presented the tutorial for a team specialized in Amphibians,
we tailored the examples using frogs and their allies.

@@

We published the tutorials on a public, free license, free of cost, and free for
use and reuse repository and persistent website \citep{RopentreeTutorials, RopentreeTutorialsWebsite}.
The tutorial is available for the users to go back to any time they need it,
and to be passed on to other users (Figure \ref{fig:second}).

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig2.png}
\end{center}
\caption{Snapshot of the home to our tutorial website, showing part of the schedule. \label{fig:second}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig-tree.png}
\end{center}
\caption{A phylogenetic tree from our tutorial website, extracted using OpenTree of Life tools and the rotl R package. \label{fig:tree}}
\end{figure}

@@

A practice that has become more and more widespread in programming-language pedagogical practices
is the use of typos and mistakes to normalize them for learners, and show them how
to solve them when they are outside the classroom \citep{shannon2015live}.
Yet, this is rarely done on written pedagogical materials.
Primary documentation focuses on demonstrating usage function with examples that
work seamlessly, without errors. We argue that the opposite is needed to support
adoption of reproducible workflows and support long term independence in learners
\citep{gaspar2007restoring}.
We demonstrate examples that do not work
as expected and exemplify ways to address them (Figure \ref{fig:error
}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig-error.png}
\end{center}
\caption{Snapshot of a section of the tutorial website, where we demonstrate a common error. \label{fig:error}}
\end{figure}

@@

Besides avoiding formal language, and incorporating elements of pop culture, such as picture
character icons known as ``emojis``, to make the language more familiar to a
broader target audience (see Figure \ref{fig:error}), we made an effort to specifically
complement the primary documentation by identifying
computational concepts that were assumed or were not explained in depth.
We vetted the tutorials through feedback from workshop participants as well as individual users.
We choose examples that are charismatic for the audience.
For example, when we presented the tutorial for a team specialized in Amphibians,
we tailored the examples using frogs and their allies.

@@

We published the tutorials on a public, free license, free of cost, and free for
use and reuse repository and persistent website \citep{RopentreeTutorials, RopentreeTutorialsWebsite}.
The tutorial is available for the users to go back to any time they need it,
and to be passed on to other users (Figure \ref{fig:schedule}).

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig-schedule.png}
\end{center}
\caption{Snapshot of the home to our tutorial website, showing part of the schedule. \label{fig:schedule}}
\end{figure}
